### 2021-04-19 paper/ase21/intro.tex
Revised Sec. 1

JavaScript is one of the most popular programming languages.  According to the
2020 State of the Octoverse\footnote{https://octoverse.github.com/}, which is
the annual report of GitHub, the most dominated programming language in GitHub
repositories was JavaScript since 2014 to 2020.  While JavaScript was initially
designed for client-side programming in web browsers, now it is widely used in
server-side programming~\cite{nodejs} and even in embedded
systems~\cite{espruino, tessel2, moddable}.  Thus, its engines are also
developed and maintained in diverse fields conforming to ECMAScript, the
JavaScript standard specification that describes the syntax and semantics of
JavaScript.

The correctness of ECMAScript becomes more important because an incorrect
description of syntax or semantics in the specification can lead to the wrong
implementation of existing JavaScript engines used in various fields.  However,
all the specification updates are currently manually checked by the Ecma
Technical Committee 39 (TC39) without any automated tools.  This manual checking
process is obviously labor-intensive and also error-prone thus the current
JavaScript specification is vulnerable to specification bugs.  Besides, in late
2014, the committee announced yearly release cadence and open development
process of ECMAScript to quickly adapt to an evolving development environment.
According to \citet{jiset}, the average number of updated steps of abstract
algorithms between consecutive releases from ECMAScript 2016 (ES7) to 2019
(ES10) is 9645.5.  In the official repository of ECMAScript, \inred{1,355} pull
requests and \inred{2,005} commits exist in the master branch.  Therefore, it
makes more difficult to manually check all the specification updates using
limited human resources.

Unfortunately, there is no existing tool to automatically detect bugs in the
rapidly evolved JavaScript specifications.  Thus, the committee of ECMAScript
have tried to resolve this problem using additional annotations in abstract
algorithms.  Additional annotations make the specification more readable and
also they are useful for the specification-based tools such as JavaScript
engines~\cite{v8, graaljs, qjs, moddable}, debuggers~\cite{jsexplain}, static
analyzers~\cite{safe, tajs, jsai, wala}, and verification tools~\cite{javert,
javert2}.  Thus, they decided to manually insert two different annotations: 1)
\textit{assertions} to denote the assumptions in a certain point of abstract
algorithms, and 2) two different \textit{prefixes} \textbf{?} and \textbf{!} to
represent whether completion records might be abrupt or not.  For example,
``Assert: Type(\textit{O}) is Object'' denotes that the variable $\textit{O}$
always has an \jscode{Object} value at this point and ``\textbf{?}
\textbf{GetV}(\textit{V}, \textit{P})'' denotes that return values of
\textbf{GetV}(\textit{V}, \textit{P}) might be abrupt completions and directly
return them if they are.  Moreover, they recently started the internal
discussion of manual type annotations for variables, parameters, and return
values for each abstract algorithm
\footnote{https://github.com/tc39/ecma262/pull/545\#issuecomment-559292107}.
However, to manually annotate types for all of them without any automated tool
is also labor-intensive and error-prone.  Furthermore, even though such manual
type annotations can give more information for manual checking of specification
updates, it still does not provide any automatic mechanism to detect
specification bugs.

To alleviate this problem, we propose a tool $\tool$, a \textbf{J}avaScript
\textbf{S}pecification \textbf{T}ype \textbf{A}nalyzer using
\textbf{R}efinement.  The main idea of our tool is to perform \textit{type
analysis} for JavaScript specifications to statically detect type-related
specification bugs in an automatic way.  However, it is difficult to directly
perform type analysis to ECMAScript because its abstract algorithms are written
in a natural language.  For a decade, researchers~\cite{lambdajs, jscert, kjs}
have tried to formally define various JavaScript semantics for a specific
version of ECMAScript by hand.  However, the manual formalization is not
suitable for the automatic detection of bugs in the rapidly evolved JavaScript
specifications.  To lessen such burden, several approaches to utilize
information directly extracted from specifications written in a natural language
are recently presented in diverse fields including system
architectures~\cite{x86, arm}, network protocols~\cite{basespec}, and language
specifications~\cite{spectest, javadoc}.  For JavaScript, \citet{jiset} presents
$\jiset$ that automatically compiles each abstract algorithm written in a
structured natural language to the corresponding function of $\ires$, an untyped
intermediate representation for ECMAScript.  Therefore, we utilize this tool to
mechanically handle JavaScript specifications.

For the compiled mechanized specifications, $\tool$ performs type analysis for
compiled functions with specification types defined in ECMAScript.  ECMAScript
contains not only JavaScript language types but also specification types such as
abstract syntax trees (ASTs), internal records (e.g. environments, completions,
or property descriptors), and internal list-like structures.  We define their
type hierarchy and fields based on type-related tables in ECMAScript and
automatically extracted syntax-directed algorithms.  Based on such type
information, $\tool$ performs type analysis and detects specification bugs using
a \textit{bug detector} consisting of four different checkers: 1) reference
checker, 2) arity checker, 3) assertion checker, and 4) operand checker.
Moreover, to increase precision of type analysis, we also present a
\textit{condition-based refinement} for type analysis on ECMAScript. Its main
concept is to prune out infeasible parts in abstract states by using conditions
of assertions and branches.  The refinement technique can reduce the number of
false bugs caused by spurious types inferred by imprecise analysis.  We evaluate
our tool with all \inred{864} different versions existed in the official
ECMAScript repository for the recent three years from 2018 to 2021.

In summary, our main contributions are as follows:
\begin{itemize}
  \item We present $\tool$, which is the first tool that performs \textit{type
    analysis} on ECMAScript to check the correctness of JavaScript language
    specifications.  $\tool$ automatically detects type-related specification
    bugs via the \textit{bug detector} consisting of four different checkers: 1)
    reference checker, 2) arity checker, 3) assertion checker, and 4) operand
    checker.
  \item We present a \textit{condition-based refinement} for type analysis of
    ECMAScript to reduce the number of false bugs by increasing the analysis
    precision.  We show that the refinement technique increase the analysis
    precision from \inred{30.4}\% to \inred{52.0}\% by removing \inred{122}
    false bugs and detecting \inred{one} more true bug.
  \item We demonstrate the practicality of $\tool$. It takes \inred{136.1}
    seconds on average to perform type analysis for each version, and detected
    \inred{177} type-related specification bugs with \inred{52.0}\% precision;
    \inred{92} out of \inred{177} bugs are true bugs.  Among them, \inred{14}
    bugs are newly detected by $\tool$ and the committee confirmed all of them.
\end{itemize}

>>>>

JavaScript is one of the most popular programming languages.  According to the
2020 State of the Octoverse\footnote{https://octoverse.github.com/},
the annual report of GitHub, the most dominating programming language in GitHub
repositories was JavaScript since 2014 to 2020.  While JavaScript was initially
designed for client-side programming in web browsers, it is now widely used in
server-side programming~\cite{nodejs} and even in embedded
systems~\cite{espruino, tessel2, moddable}.  Developers in diverse fields
build and maintain JavaScript engines conforming to ECMAScript, the
JavaScript standard specification, which describes the syntax and semantics of
JavaScript in a natural language.

The correctness of ECMAScript is critical because an incorrect
description in the specification can lead to wrong
implementations of JavaScript engines in various fields.  However,
all the specification updates are currently manually reviewed by the Ecma
Technical Committee 39 (TC39) without any automated tools.
Such a manual review process is inherently labor-intensive and error-prone,
making ECMAScript vulnerable to specification bugs.
Besides, in late 2014, the committee announced the yearly release cadence and open development
process of ECMAScript to quickly adapt to evolving development environments.
According to \citet{jiset}, the average number of updated steps of abstract
algorithms between consecutive releases from ECMAScript 2016 (ES7) to 2019 (ES10) is 9645.5.
In the official ECMAScript repository, \inred{1,355} pull
requests and \inred{2,005} commits exist in the master branch.
Therefore, manually checking all the frequent specification updates is
a challenging task.

Unfortunately, no existing tools can automatically detect bugs in
rapidly evolving JavaScript specifications written in English. Thus,
the ECMAScript committee has pursued various manual annotations in
abstract algorithms to reduce specification bugs.
First, the committee has introduced two kinds of annotations: 1)
\textit{assertions} to denote assumptions at specific points of abstract
algorithms and 2) two \textit{prefixes} \textbf{?} and \textbf{!} to
represent whether the execution of an abstract algorithm completes
abruptly or not. For example, ``Assert: Type(\textit{O}) is Object'' denotes that
the variable $\textit{O}$ always has an \jscode{Object} value at the
point of the assertion, and ``\textbf{?} \textbf{GetV}(\textit{V}, \textit{P})'' denotes that
the execution of \textbf{GetV}(\textit{V}, \textit{P}) may complete abruptly.
Such annotations help readers understand specifications clearly, and
they are also helpful for specification-based tools such as JavaScript
engines~\cite{v8, graaljs, qjs, moddable}, debuggers~\cite{jsexplain}, static
analyzers~\cite{safe, tajs, jsai, wala}, and verification tools~\cite{javert,
javert2}\footnote{https://github.com/tc39/ecmarkup/issues/173}.
Second, the committee has started internal discussions on type
annotations for variables, parameters, and return values of abstract
algorithms\footnote{https://github.com/tc39/ecma262/pull/545\#issuecomment-559292107}.
However, any kinds of manual annotations are labor-intensive and
error-prone, and they do not provide any automatic mechanism to detect
specification bugs.

To alleviate this problem, we propose a tool $\tool$, a \textbf{J}avaScript
\textbf{S}pecification \textbf{T}ype \textbf{A}nalyzer using
\textbf{R}efinement. In order to perform a \textit{type analysis} on ECMAScript
to statically detect type-related specification bugs automatically,
the main challenge is that ECMAScript describes abstract algorithms in
a natural language, English. While researchers~\cite{lambdajs, jscert, kjs}
have formally defined various JavaScript semantics for different
versions of ECMAScript by hand, manual formalization is not suitable for
automatically detecting bugs in rapidly evolving JavaScript specifications. 
Thus, recent approaches in diverse fields such as system architectures~\cite{x86, arm},
network protocols~\cite{basespec}, and language specifications~\cite{spectest, javadoc}
have utilized information directly extracted from specifications written in a natural language
to lessen such burdens.
Among them, $\jiset$~\cite{jiset} compiles ECMAScript abstract algorithms written in
a structured natural language to functions in $\ires$, an untyped
intermediate representation for ECMAScript.
Therefore, $\tool$ can handle JavaScript specifications mechanically using $\jiset$.

For mechanized JavaScript specifications by $\jiset$, $\tool$ performs
a type analysis of compiled functions using \textit{specification types}
defined in ECMAScript. ECMAScript contains not only JavaScript
language types but also specification types such as abstract syntax
trees (ASTs), internal list-like structures, and internal records
including environments, completions, and property descriptors. We
define their type hierarchies and fields based on the type-related
tables in ECMAScript and automatically extracted syntax-directed algorithms.
Using such type information, $\tool$ performs a type analysis and detects specification bugs using
a \textit{bug detector} consisting of four checkers: 1) a reference
checker, 2) an arity checker, 3) an assertion checker, and 4) an operand checker.
$\tool$ also uses a \textit{condition-based refinement} for type
analysis, which prunes out infeasible parts in abstract states by using conditions
of assertions and branches to improve the precision of type analysis.
We evaluated $\tool$ with all \inred{864} versions in the official
ECMAScript repository for the recent three years from 2018 to 2021.
The experiments showed that the refinement technique could reduce the number of
false-positive bugs caused by spurious types inferred by imprecise type analysis.

The main contributions of this paper are as follows:
\begin{itemize}
  \item We present $\tool$, the first tool that performs a \textit{type
    analysis} on ECMAScript written in a natural language to check the correctness of JavaScript language
    specifications.  $\tool$ automatically detects type-related specification
    bugs such as unknown variables, duplicated variables, missing
    parameters, assertion failures, ill-typed operands, and unchecked
    abrupt completion bugs.
  \item We present a \textit{condition-based refinement} for type analysis of
    ECMAScript to reduce the number of false-positive bugs by enhancing the analysis
    precision.  We show that the refinement technique increases the analysis
    precision from \inred{30.4}\% to \inred{52.0}\% by removing \inred{122}
    false bugs and detecting \inred{one} more true bug.
  \item We demonstrate the practicality of $\tool$. It takes \inred{136.1}
    seconds on average to perform a type analysis for each version of ECMAScript and detected
    \inred{177} type-related specification bugs with \inred{52.0}\% precision;
    \inred{92} out of \inred{177} bugs are true bugs.  Among them, $\tool$ 
    newly detected \inred{14} bugs, and the ECMAScript committee confirmed them all.
\end{itemize}
